Generalized Tractability

### 2023-06-04 GeneralizedTractability_230529.tex
Updates from Overleaf

Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d,\vp)$ are non-decreasing in $i$ for $i \in \{1, \ldots, M(d)+1\}$. In particular, for any \peter{$N\in\{1,\ldots,M(d)\}$ and any} $n \in \{N, \ldots, M(d)\}$
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d,\vp)} \\
     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp) }
    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) }
    \le \frac{1}{n-N+1} \sum_{i=N}^{M(d)}  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline} \label{eq:implicate_a_rest}
    n - N +1 \ge T(\varepsilon^{-1},d,\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le
   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) } \le \frac{1}{T(\varepsilon^{-1},d,\vp)} \\ \forall d, n, N \in \naturals.
\end{multline}
We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer and $n - N +1$ is assumed to be positive.

@@

This upper bound on $i$ in terms of $T(\lambda_{i,d}^{-1},d,\vp)$ implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
\[
	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
	[T(\lambda_{i,d}^{-1},d, \vp)]^\tau
	\ge
	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad  \forall i\in I_{d},  \ d \in \naturals.
 \]
To carry the argument further, we need to show that the interval $I_d$ contains the interval
\[
\tI_{d}:=\begin{cases} 
\{i(\infty,d,\vp),\ldots, M(d)\}, & E(d) > 0, \\
\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
\end{cases}
\]

Since $I_d = \tI_d$ when $E(d) =0$, we need only consider the case where $E(d) > 0$.  In this case \eqref{eq:Mddef} and \eqref{eq:lambda_K4} imply that
\[
\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+2} \le E(d) < \lambda_{M(d)+1,d}.
\]
This means that $i(E(d),d,\vp)-1 \ge M(d)+1$, and so $I_d \ge \tI_d$

\[
\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+2} \le E(d) < \lambda_{M(d)+1,d} 
\]

Choose an $\varepsilon \in (E(d),\infty)$ such that $i(\varepsilon,d,\vp) = i(E(d),d,\vp) - 1$.  It follows from \eqref{eq:lambda_K4} that
\[
\lambda_{i(\varepsilon,d,\vp)} \le \varepsilon < E(d) \le \lambda_{i(\varepsilon,d,\vp)} + 1
\]

Note that, for any $\delta>0$,
\[
\lambda_{\lfloor C_{\vp}\, T((E(d) + \delta)^{-1},d,\vp)\rfloor +1} \le E(d) + \delta, 
\]
\peter{Furthermore, define
\[
i (E(d),d,\vp):=\lim_{\delta\to 0}\, i (E(d)+\delta,d,\vp)
= \lim_{\delta\to 0}\, \lfloor C_{\vp}\, T((E(d) + \delta)^{-1},d,\vp)\rfloor +1. 
\]
Note that, for any $\delta>0$,
\[
\lambda_{\lfloor C_{\vp}\, T((E(d) + \delta)^{-1},d,\vp)\rfloor +1} \le E(d) + \delta, 
\]
and therefore, for $\delta\to 0$, we obtain
\[
\lambda_{i (E(d),d,\vp)} \le E(d). 
\]
On the other hand, by definition of $M(d)$, $M(d)$ is minimal such that 
\[
\lambda_{M(d)+2}\le E(d).
\]
This implies that 
\[
M(d) < M(d) +2 \le i (E(d),d,\vp).
\]

}

For $\varepsilon$ taking on all \peter{values in $(E(d),\infty)$}, $i(\varepsilon,d,\vp)$ takes on all values 
\peter{in 
\[
I_{E(d),d}:=\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)\}
\]
} 
so
\[
i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \peter{\forall i\in I_{E(d),d}},  \ d \in \naturals.
\]

This implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
\[
	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
	[T(\lambda_{i,d}^{-1},d, \vp)]^\tau
	\ge
	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad  \peter{\forall i\in I_{E(d),d}},  \ d \in \naturals,
 \]
 and this implies
 \[
	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad  \peter{\forall i\in 
 \{i(\infty,d,\vp)+1,\ldots, M(d)\}},  \ d \in \naturals.
\]

>>>>

Define the interval
\begin{equation} \label{eq:hIdef}
\hI_{d}:=\begin{cases} 
\{1,\ldots, M(d)\}, & M(d) < \infty, \\
\naturals, & M(d) = \infty.
\end{cases}
\end{equation}
Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{\cdot,d}^{-1},d,\vp)$ is non-decreasing. For any $N\in \hI_d$ and any $n \in \hI_d \setminus \{1, \ldots, N-1\}$,
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d,\vp)} \\
     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp) }
    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) }
    \le \frac{1}{n-N+1} \sum_{i=N}^{M(d)}  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline} \label{eq:implicate_a_rest}
    n - N +1 \ge T(\varepsilon^{-1},d,\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le
   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) } \le \frac{1}{T(\varepsilon^{-1},d,\vp)} \\ \forall d \in \naturals, \ N \in \hI_d, \ n \in \hI_d \setminus \{1, \ldots, N-1\}.
\end{multline}
We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer and $n - N +1$ is assumed to be positive.

@@

This upper bound on $i$ in terms of $T(\lambda_{i,d}^{-1},d,\vp)$ implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
\begin{equation}\label{eq:restrictKfive}
	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
	[T(\lambda_{i,d}^{-1},d, \vp)]^\tau
	\ge
	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad  \forall i\in I_{d},  \ d \in \naturals.
 \end{equation}
To carry the argument further, we need to show that the interval $I_d$ contains the interval
\[
\tI_{d}:=\begin{cases} 
\{i(\infty,d,\vp),\ldots, M(d)\}, & E(d) > 0, \\
\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
\end{cases}
\]

Since $I_d = \tI_d$ when $E(d) =0$, we need only consider the case where $E(d) > 0$.  In this case \eqref{eq:Mddef} and \eqref{eq:lambda_K4} imply that
\[
\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+2} \le E(d) < \lambda_{M(d)+1,d}.
\]
This means that $i(E(d),d,\vp)-1 \ge M(d)+1$, and so $I_d \supseteq \tI_d$.

 and this implies
 \[
	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad  \peter{\forall i\in 
 \{i(\infty,d,\vp)+1,\ldots, M(d)\}},  \ d \in \naturals.
\]
